PyPy's Approach to Virtual Machine Construction

### 2006-05-31 talk/dls2006/paper.tex
Clarify this paragraph (thanks mwh)

\item the Python objects that emulate instances of these types.  (More
      about them below.)
\end{enumerate}
%
We have defined well-typed operations between variables of these types,
plugging on the standard Python operators.  These operations are the
ones that the emulating instances implement.  As seen above, the types
can also be used by type inference when analysing system code like the
helpers of figure \ref{fig_llappend}.

>>>>

\item the Python objects that emulate instances of these types.  (More
      about them below.)
\end{enumerate}
%
We have defined well-typed operations between instances of these types,
syntactically expressed with standard Python operators (e.g.\ if \texttt{x}
is a C-level array, \texttt{x[n]} accesses its \texttt{n}th item).
The emulating instances provide a concrete implementation of
these operations that works in normal Python; the types involved in the
operations are also known to the type inference engine when it
analyses system code like the helpers of figure \ref{fig_llappend}.
